### 2016-05-09 ch03-lrm/nonparametric.tex
Press for low SNR

For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
The values of the \gls{PRESS} are again very noisy.
\TODO{PRESS is eigenlijk niet bruikbaar bij lage SNR}

>>>>

For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
The values of the \gls{PRESS} are again very noisy, especially for the \gls{LPM} estimates.
Near the resonance, the $\lrm{7,1,1,1}$ results in the smalles \gls{PRESS} value.
This is in correspondence with the observations of the variance for similar noise levels in \figref{fig:nparam:comparison:terribleSNR}.
Note however that the results do not carry over to the \gls{RMS} error: since the \gls{LRM} is severely biased, the \gls{PRESS} becomes unreliable to detect model errors.
